Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by organization x.}

### 2018-08-10 paper.tex
Sections 1 and 2 are in habitable order (except for the missing intro)

\keywords{Bigraphs \and Bigraphical reactive systems \and Probabilistic
  semantics \and Discrete-time Markov chain \and Markov decision process \and
  Spatial models.}
\end{abstract}

@@

TODO: DTMC generation, MDP generation: show, define

@@

% TODO: rework, transition from brs to bigraph
Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
universal formalism for modelling interacting systems that evolve in time and
space. In this paper we use a generalised version of bigraphs, known as
\emph{bigraphs with sharing}
\cite{DBLP:phd/ethos/Sevegnani12,dblp:journals/tcs/sevegnanic15}, that uses
directed acyclic graphs instead of forests to represent node placement, allowing
one node to be contained in the intersection of several other nodes. In this
section we introduce the main concepts and definitions in order to expand on
them in Section~\ref{extensions}.

@@

Informally, a bigraph can be thought of as a graph, where a node can be inside
another node (in this case it can even be in an intersection of several nodes).
However, the pictures tend to become much clearer if we instead visualise the
nesting relations between nodes as just a different type of edges. Consider the
bigraph in Fig.~\ref{example_bigraph}. The white ellipses are the \emph{nodes}.
Each node has a type, called \emph{control}, and denoted here by the labels
$\mathsf{A}, \mathsf{B}$, and $\mathsf{C}$. The green edges are actually
hyperedges (can connect any positive number of nodes), and are called
\emph{links}. In this example they are given names $\mathsf{x}, \mathsf{y}$, and
$\mathsf{e}$. Each node has an ordered list of \emph{ports} (not pictured in
the diagram) that can be thought of as sockets for links. Nodes of the same
control have the same number of ports. The number of ports a node of control
$\mathsf{K}$ can have is called the \emph{arity} of $\mathsf{K}$ and is denoted
by $\ar(\mathsf{K})$. The two white dashed rectangles represent \emph{regions},
and in this representation are the parents to any otherwise parentless nodes.
Grey dashed rectangles are called \emph{sites}, and encode parts of the model
that have been abstracted away. Nodes, sites, and regions are also known as
\emph{places}. The directed black arrows between places show the containment
relations, e.g., the $\mathsf{A}$ node has two children (inner nodes):
$\mathsf{B}$ and the only site in this bigraph, labelled by the number $0$.

@@

\section{Extensions to Bigraphs} \label{extensions}

\subsection{Probabilistic Bigraphs}

@@

\subsection{Nondeterministic Bigraphs}

>>>>

\keywords{Bigraphs \and Bigraphical reactive systems \and Probabilistic
  semantics \and Markov decision process \and Spatial models.}
\end{abstract}

@@

% TODO: introduction
%Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
%universal formalism for modelling interacting systems that evolve in time and
%space.

%TODO: MDP generation: show, define

@@

@@

Informally, a bigraph can be thought of as a graph, where a node can be inside
another node\footnote{To be specific, in this paper we extend the ideas behind
  \emph{bigraphs with sharing}
  \cite{DBLP:phd/ethos/Sevegnani12,dblp:journals/tcs/sevegnanic15}, where a node
  can be contained in the intersection of several other nodes.}. However, the
pictures tend to become much clearer if we instead visualise the nesting
relations between nodes as just a different type of edges. Consider the bigraph
in Fig.~\ref{example_bigraph}. The white ellipses are the \emph{nodes}. Each
node has a type, called \emph{control}, and denoted here by the labels
$\mathsf{A}, \mathsf{B}$, and $\mathsf{C}$. The green edges are actually
hyperedges (can connect any positive number of nodes), and are called
\emph{links}. In this example they are given names $\mathsf{x}, \mathsf{y}$, and
$\mathsf{e}$. Each node has an ordered list of \emph{ports} (not pictured in the
diagram) that can be thought of as sockets for links. Nodes of the same control
have the same number of ports. The number of ports a node of control
$\mathsf{K}$ can have is called the \emph{arity} of $\mathsf{K}$ and is denoted
by $\ar(\mathsf{K})$. The two white dashed rectangles represent \emph{regions},
and in this representation are the parents to any otherwise parentless nodes.
Grey dashed rectangles are called \emph{sites}, and encode parts of the model
that have been abstracted away. Nodes, sites, and regions are also known as
\emph{places}. The directed black arrows between places show the containment
relations, e.g., the $\mathsf{A}$ node has two children (inner nodes):
$\mathsf{B}$ and the only site in this bigraph, labelled by the number $0$.

@@

\section{Extensions to BRSs} \label{extensions}

We propose two new BRSs: one adds probabilities to reaction rules, the other
also groups the rules into actions and supports rewards based on both reaction
rules and predicates. The main technicality in both the definitions and the
implementation is that after generating a list of applicable ground reaction
rules (for a particular action, if appropriate), the probabilities need to be
normalised so that they add to $1$, as a single reaction rule can sometimes be
applied in multiple places, or some rules in an action may not be applicable.

\subsection{Probabilistic BRS}

@@

\subsection{Nondeterministic BRS}
